---
title: "R draw unrooted cluster trees"
output:
  github_document: default
  html_document:
    df_print: paged
---
Note because Seurat Object was made with Seurat 4.0 it doesn't have format needed (SCT feature models) for BuildClusterTree in Seurat v4.3.  So running in renv with Seurat v 4.0.5.

```{r libraries, results=F}
library(Seurat)
library(Signac)
library(dplyr)
library(ggplot2)
library(ggsci)
options(future.globals.maxSize = 4000 * 1024^2)
```

# Read data
```{r readdata.10}
E10hpf <- readRDS("~/Documents/Projects/Sagerstrom/CHB_SC_r6_manuscript/data/HB10hpf_neural.RDS")
Idents(E10hpf) <- "Clusters"
DefaultAssay(E10hpf) <- "SCT"
DimPlot(E10hpf, reduction = "wnn.umap") + scale_color_igv()
```

Rename CHB and SC clusters to match HB13hpf and correct CHB.1 to SC.  See Match_CHB_SC_Cluster_Names.
```{r rename_HB10}
Idents(E10hpf) <- "Clusters"
E10hpf <- RenameIdents(E10hpf,
                    "SC.1" = "oldSC.1",
                    "SC.2" = "oldSC.2",
                    "SC.3" = "oldSC.3")
E10hpf <- RenameIdents(E10hpf,
                    "CaudHB.1" = "SC.1a",
                    "CaudHB.2" = "CHB.1",
                    "CaudHB.3" = "CHB.2",
                    "oldSC.1" = "SC.3a",
                    "oldSC.2" = "SC.1b",
                    "oldSC.3" = "SC.3b")
DimPlot(E10hpf, reduction = "wnn.umap") + scale_color_igv()
```

No need to rename HB13hpf clusters since CHB and SC cluster numbers based on HB13hpf dataset.

```{r readdata.13}
HB13hpf <- readRDS("~/Documents/Projects/Sagerstrom/CHB_SC_r6_manuscript/data/HB13hpf_neural.RDS")
Idents(HB13hpf) <- "Clusters"
DimPlot(HB13hpf, reduction = "wnn.umap") + scale_color_igv()
```

```{r readdata.16}
HB16hpf <- readRDS("~/Documents/Projects/Sagerstrom/CHB_SC_r6_manuscript/data/HB16hpf_neural.RDS")
Idents(HB16hpf) <- "Clusters"
DimPlot(HB16hpf, reduction = "wnn.umap") + scale_color_igv()
```

Rename CHB and SC clusters to match HB13hpf. See Match_CHB_SC_Cluster_Names

```{r rename_HB16}
Idents(HB16hpf) <- "Clusters"
HB16hpf <- RenameIdents(HB16hpf,
                     "CHB.1" = "oldCHB.1",
                     "CHB.2" = "oldCHB.2",
                     "CHB.3" = "oldCHB.3",
                     "CHB.4" = "oldCHB.4",
                     "SC.2" = "oldSC.2",
                     "SC.3" = "oldSC.3")
HB16hpf <- RenameIdents(HB16hpf,
                     "oldCHB.1" = "CHB.3",
                     "oldCHB.2" = "CHB.1",
                     "oldCHB.3" = "CHB.2",
                     "oldCHB.4" = "CHB.1",
                     "oldSC.2" = "SC.3",
                     "oldSC.3" = "SC.2")
DimPlot(HB16hpf, reduction = "wnn.umap") + scale_color_igv()
```


# Build and Plot Cluster Trees
```{r dendogram.10}
E10hpf <- BuildClusterTree(E10hpf, graph = "wsnn", slot = "scale.data")
data.tree.10 <- Tool(object = E10hpf, slot = "BuildClusterTree")
png(filename = "Plots/E10hpf_dendogram.png",width = 8, height = 8, units = "in", res=1200)
p1 <- ape::plot.phylo(x = data.tree.10,  use.edge.length = FALSE, cex = 0.5, type = "u")
p1
dev.off()
png(filename = "Plots/E10hpf_dendogram_vs2.png",width = 8, height = 8, units = "in", res=1200)
p2 <- ape::plot.phylo(x = data.tree.10,  use.edge.length = FALSE, cex = 0.8, type = "u", lab4ut = "axial")
p2
dev.off()
```

```{r dendogram.13}
HB13hpf <- BuildClusterTree(HB13hpf, graph = "wsnn", slot = "scale.data")
data.tree.13 <- Tool(object = HB13hpf, slot = "BuildClusterTree")
png(filename = "Plots/HB13hpf_dendogram.png",width = 8, height = 8, units = "in", res=1200)
p1 <- ape::plot.phylo(x = data.tree.13,  use.edge.length = FALSE, cex = 0.5, type = "u")
p1
dev.off()
png(filename = "Plots/HB13hpf_dendogram_vs2.png",width = 8, height = 8, units = "in", res=1200)
p2 <- ape::plot.phylo(x = data.tree.13,  use.edge.length = FALSE, cex = 0.8, type = "u", lab4ut = "axial")
p2
dev.off()
```

```{r dendogram.16}
HB16hpf <- BuildClusterTree(HB16hpf, graph = "wsnn", slot = "scale.data")
data.tree.16 <- Tool(object = HB16hpf, slot = "BuildClusterTree")
png(filename = "Plots/HB16hpf_dendogram.png",width = 8, height = 8, units = "in", res=1200)
p1 <- ape::plot.phylo(x = data.tree.16,  use.edge.length = FALSE, cex = 0.5, type = "u")
p1
dev.off()
png(filename = "Plots/HB16hpf_dendogram_vs2.png",width = 8, height = 8, units = "in", res=1200)
p2 <- ape::plot.phylo(x = data.tree.16,  use.edge.length = FALSE, cex = 0.8, type = "u", lab4ut = "axial")
p2
dev.off()
```

```{r sessioninfo}
sessionInfo()
```

