---
title: "R Match CHB cluster names between samples so CHB.1 et al are the same cell type in each"
output:
  html_document:
    df_print: paged
  github_document: default
---

```{r libraries}
suppressPackageStartupMessages({
  library(Seurat)
  library(Signac)
  library(BSgenome.Drerio.UCSC.danRer11)
  library(EnhancedVolcano)
  library(ggsci)
  library(patchwork)
  library(dplyr)
})
```

# Read data
```{r read_E10}
E10 <- readRDS(file = "../data/HB10hpf_neural.RDS")
DefaultAssay(E10) <- "SCT"
Idents(E10) <- "Clusters"
```

```{r read_HB13}
HB13 <- readRDS(file = "../data/HB13hpf_neural.RDS")
DefaultAssay(HB13) <- "SCT"
Idents(HB13) <- "Clusters"
```

```{r read_HB16}
HB16 <- readRDS(file = "../data/HB16hpf_neural.RDS")
DefaultAssay(HB16) <- "SCT"
Idents(HB16) <- "Clusters"
```

```{r read_int}
HB.int <- readRDS(file = "../data/int.neural.3WT.subset.RDS")
DefaultAssay(HB.int) <- "SCT"
Idents(HB.int) <- "intClusters"
```

# Cluster names

## E10hpf

Named clusters after clustering at resolution 8, needed to resolve all rhombomeres into separate clusters.
```{r umap_E10}
DimPlot(E10, reduction = "wnn.umap") + scale_color_igv()
```
Combining multiple clusters of same cell type.
```{r rename_E10}
Idents(E10) <- "Clusters"
E10 <- RenameIdents(E10,
                    "FB & eye.1" = "FB & eye",
                    "FB &  eye.2" = "FB & eye",
                    "FB & eye.3" = "FB & eye",
                    "FB & eye.4" = "FB & eye",
                    "FB & eye.5" = "FB & eye",
                    "FB & eye.6" = "FB & eye",
                    "FB & eye.7" = "FB & eye",
                    "FB & eye.8" = "FB & eye",
                    "FB.1" = "FB",
                    "MB.1" = "MB",
                    "CaudHB.1" = "CHB.1",
                    "CaudHB.2" = "CHB.2",
                    "CaudHB.3" = "CHB.3",
                    "MHB.1" = "MHB",
                    "MHB.2" = "MHB",
                    "MHB.3" = "MHB")
levels(E10) <- c("FB & eye","FB","MB","MHB","HB.1","HB.2","HB.3","CHB.1","CHB.2","CHB.3",
                 "SC.1","SC.2","SC.3","NC.1","NC.2")
umap.E10 <- DimPlot(E10, reduction = "wnn.umap") + scale_color_igv() + 
  guides(color = guide_legend(override.aes = list(size=4), ncol=2) )
umap.E10
```

## HB13hpf

Named clusters after clustering at resolution 8, needed to resolve all rhombomeres into separate clusters.
```{r umap_HB13}
DimPlot(HB13, reduction = "wnn.umap") + scale_color_igv()
```
Combining multiple clusters of same cell type.
```{r rename_HB13}
Idents(HB13) <- "Clusters"
HB13 <- RenameIdents(HB13,
                       "r5.1" = "r5",
                       "r5.2" = "r5",
                       "MB.1" = "MB",
                       "MB.2" = "MB",
                       "MB.3" = "MB",
                       "MHB.1" = "MHB",
                       "MHB.2" = "MHB",
                       "MHB.3" = "MHB",
                       "MHB.4" = "MHB",
                       "MHB.5" = "MHB",
                       "FB.1" = "FB",
                       "FB.2" = "FB",
                       "FB.3" = "FB",
                       "FB.4" = "FB")
levels(HB13) <- c("FB","MB","MHB","r1","r1 & r2","r2","r3","r4","r5","r6",
                    "low_expression","unknown","Neuron","Ciliated","CHB.1","CHB.2","CHB.3","SC.1","SC.2","SC.3")
umap.HB13 <- DimPlot(HB13, reduction = "wnn.umap") + scale_color_igv() + 
  guides(color = guide_legend(override.aes = list(size=4), ncol=2) )
umap.HB13
```

## HB16hpf
Named clusters after clustering at resolution 6, needed to resolve all rhombomeres into separate clusters.
```{r umap_HB16}
DimPlot(HB16, reduction = "wnn.umap") + scale_color_igv()
```
Combining multiple clusters of same cell type.
```{r rename_HB16}
Idents(HB16) <- "Clusters"
HB16 <- RenameIdents(HB16,
                       "r5.1" = "r5",
                       "r5.2" = "r5",
                       "MB.1" = "MB",
                       "MB.2" = "MB",
                       "MHB.1" = "MHB",
                       "MHB.2" = "MHB",
                       "MHB.3" = "MHB")
levels(HB16) <- c("FB","MB","MHB","r1","r2","r3","r4","r5","r6",
                    "DorsNT & NC","Neuron","Ciliated","CHB.1","CHB.2","CHB.3","CHB.4","SC.1","SC.2","SC.3")
umap.HB16 <- DimPlot(HB16, reduction = "wnn.umap") + scale_color_igv() + 
  guides(color = guide_legend(override.aes = list(size=4), ncol=2) )
umap.HB16
```
## HB integrated

```{r table1}
table(HB.int$intClusters, HB.int$orig.ident)
```

```{r rename_HBint}
Idents(HB.int) <- "intClusters"
HB.int <- RenameIdents(HB.int,
                       "r1&r2.1" = "r1 & r2",
                       "r1&r2.2" = "r1 & r2",
                       "r3.1" = "r3",
                       "r4.1" = "r4",
                       "r4.2" = "r4",
                       "r5.1" = "r5",
                       "r5.2" = "r5",
                       "r6.1" = "r6",
                       "r6.2" = "r6",
                       "MB.1" = "MB",
                       "MB.2" = "MB",
                       "MB.3" = "MB",
                       "MHB.1" = "MHB",
                       "MHB.2" = "MHB",
                       "MHB.3" = "MHB",
                       "MHB.4" = "MHB",
                       "MHB.5" = "MHB",
                       "MHB.6" = "MHB",
                       "Neuron.1" = "Neuron",
                       "Neuron.2" = "Neuron",
                       "CaudHB.1" = "CHB.1",
                       "CaudHB.2" = "CHB.2",
                       "CaudHB.3" = "CHB.3",
                       "CaudHB.4" = "CHB-10hpf")
levels(HB.int) <- c("MB","MHB","r1 & r2","r1","r2","r3","r4","r5","r6",           
                  "CHB.1","CHB.2","CHB.3","CHB-10hpf","SC.1","SC.2","SC.3","SC.4",
                  "Neuron","Ciliated","Neurog","NC.1","NC.2","HB","Mitochondrial")
umap.HBint <- DimPlot(HB.int, reduction = "wnn.umap") + scale_color_igv() #+ 
  #guides(color = guide_legend(override.aes = list(size=4), ncol=2) )
umap.HBint
```
```{r umap_CHB10hpf}
DimPlot(HB.int, reduction = "wnn.umap", cells.highlight = WhichCells(HB.int, idents = "CHB-10hpf"))
```

CaudHB.4 is a mix of E10hpf CaudHB cells

```{r table2}
df <- as.data.frame(table(HB.int$intClusters, HB.int$Clusters))
df[df$Var1 == "CaudHB.4" & df$Freq > 0,]
```

Get cell counts of original identities of HB.int CHB and SC cells.
```{r table3}
HB.int$sample_cluster <- paste(HB.int$orig.ident, HB.int$Clusters, sep = "_")
df2 <- as.data.frame(table(HB.int$intClusters, HB.int$sample_cluster))
df2 <- dplyr::filter(df2[df2$Freq > 0,], grepl('CaudHB|SC',Var1)) %>%
  arrange(Var1,desc(Freq))
df2
write.csv(df2, file = "Markers/HB_integrated_CHB_SC_cell_counts.csv", row.names = F)
```



```{r CHBplots, fig.width=10, fig.height=15}
E10.plotlist <- list()
for(cluster in c("CHB.1","CHB.2","CHB.3")){
  E10.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(E10, idents = cluster),"_1")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("E10", cluster, "cells"))
}
HB13.plotlist <- list()
for(cluster in c("CHB.1","CHB.2","CHB.3")){
  HB13.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(HB13, idents = cluster),"_2")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("HB13", cluster, "cells"))
}
HB16.plotlist <- list()
for(cluster in c("CHB.1","CHB.2","CHB.3","CHB.4")){
  HB16.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(HB16, idents = cluster),"_3")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("HB16", cluster, "cells"))
}
HB16.plotlist[["spacer"]] <- plot_spacer()
HB16.plotlist[["umap"]] <- umap.HBint 
wrap_plots(c(E10.plotlist,HB13.plotlist,HB16.plotlist), ncol = 3)
```

The CHB clusters in each sample were originally numbered based on order of most cells in the cluster (following Seurat convention).  But to prevent confusion, we will base all cluster numbers to match the HB13hpf cluster numbers.

Note: E10hpf CHB.1 cells correspond to SC cluster not CHB

| HB13hpf Cluster | Sample | Cluster |
|-----------------|--------|---------|
| CHB.1           | E10    | CHB.2   |
|                 | HB16   | CHB.2/4 |
|                 | HBint  | CHB.1   |
| CHB.2           | E10    | CHB.3   |
|                 | HB16   | CHB.3   |
|                 | HBint  | CHB.2   |
| CHB.3           | E10    | none    |
|                 | HB16   | CHB.1   |
|                 | HBint  | CHB.3   |

```{r SCplots, fig.width=10, fig.height=15}
E10.plotlist <- list()
for(cluster in c("SC.1","SC.2","SC.3")){
  E10.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(E10, idents = cluster),"_1")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("E10", cluster, "cells"))
}
HB13.plotlist <- list()
for(cluster in c("SC.1","SC.2","SC.3")){
  HB13.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(HB13, idents = cluster),"_2")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("HB13", cluster, "cells"))
}
HB16.plotlist <- list()
for(cluster in c("SC.1","SC.2","SC.3")){
  HB16.plotlist[[cluster]] <- DimPlot(HB.int, reduction = "wnn.umap", 
                           cells.highlight = paste0(WhichCells(HB16, idents = cluster),"_3")) +
    scale_color_igv() + 
    NoLegend() + 
    ggtitle(paste("HB16", cluster, "cells"))
}
HB16.plotlist[["spacer"]] <- plot_spacer()
HB16.plotlist[["spacer2"]] <- plot_spacer()
HB16.plotlist[["umap"]] <- umap.HBint 
wrap_plots(c(E10.plotlist,HB13.plotlist,HB16.plotlist), ncol = 3)
```

The SC clusters in each sample were originally numbered based on order of most cells in the cluster (following Seurat convention).  But to prevent confusion, we will base all cluster numbers to match the HB13hpf cluster numbers.


| HB13hpf Cluster | Sample | Cluster |
|-----------------|--------|---------|
| SC .1           | E10    | SC.2    |
|                 | HB16   | SC.1    |
|                 | HBint  | SC.1/4  |
| SC .2           | E10    | none    |
|                 | HB16   | SC.3    |
|                 | HBint  | SC.3    |
| SC .3           | E10    | SC.1/3  |
|                 | HB16   | SC.2    |
|                 | HBint  | SC.2    |


```{r sessionInfo}
sessionInfo()
```

